\begin{Large}
\centertext{Abstract}
\end{Large}

CAD development project discuss the work done in computer-aided-design. Computer-aided design (CAD) is the use of computer systems to assist in the creation, modification, analysis, or optimization of a design.I explored FreeCAD’s source code. FreeCAD is Free and Open Source CAD Software. FreeCAD
is a fully comprehensive 3D CAD application that you can download and install for free. There is
a large base of satisfied FreeCAD users worldwide, and it is available in more than 20 languages
and for all major operating systems, including Microsoft Windows, Mac OS X and Linux (De-
bian, Ubuntu, Fedora, Mandriva, Suse ...). FreeCAD is an application for Computer Aided Design
(CAD) in three dimensions (3d). With FreeCAD you can create technical drawings such as plans
for buildings, interiors, mechanical parts or schematics and diagrams.\\

The software to be designed will create an index model for a 3 dimensional civil structure like
a building or any other civil engineering project. This requires a software for designing such
structures using a computer, the one used in SIM is STAAD PRO. In STAAD PRO the engineer
draws the structure using various graphical tools and accordingly a .STD file is created that has
all information about the building structure. Alternatively the engineer can choose to work from
this file only and creating the elements of the building by writing pre-defined instructions into the
file just like a script. It is this file that serves as the fundamental requirement for SIM. SIM parses
this file and stores the parsed information into a database which is of object orientation naturea.\\

Also, this project makes the drawings of different views of the building on the drawing sheets.
In this project, the user will be able to enter the specifications of the building through the web
browser using Django (Python Web Framework) and on the back-end, the FreeCAD macros will
use those input values to draw the drawings of different views of the building on different drawing
sheets. The output of the same can then be taken by a user in SVG, PDF and fcstd formats.\\

This project is completely open source and the entire code is available 
to the user as and when required. There is also Complete developer's 
Documentation as well as User manual alongwith it that helps using it a lot easier.
