\section{Conclusion}
SIM is a very efficient application but it does nothing but prepare notes for the design and making drawing of the building. Yes, it reads the
script, parses data out of it and then stores it in a format that the
user can easily retreat, recall and query. It can be used by Civil Engineers and M.Tech. students and even layman. It's less time consuming and user-friendly which let the User work in batch mode 
and free him from all the installation process. It is a web application that can be accessed from a number of devices. The responsive User Interface makes it easy for the users to operate it. Many efforts were made to ease the usage for the users. Hence, it is expected to be work properly in different conditions. But any future bug reports or improvements are always welcomed and will be processed happily.

I learn a lot by working on this project. During this period I got to learn a vast number of
technologies. These are listed below:
Operating system: Ubuntu
Language used: Python, C++, HTML, CSS, shellscript
Framework: Django, Materialize
Technogloy: \LaTeX{}, Djanog, Git 
Software: FreeCAD, Inkscape
So during this project I learn  all the above things. Above all I got to know how software is
developed and how much work and attention to details is required in building even the most basic
of components of any project. Planning, designing, developing code, working in a team, testing,
etc. These are all very precious lessons in themselves.
Aside from all above I got go know about various methods like -:
\begin{enumerate}
\item Embedding and using different tech in one software.
\item How to work like in group for development of software.
\end{enumerate}

Beside these technology used in project I also get to know some other tech also like -:
\begin{enumerate}
\item  Flex and Bison
\item opensshserver 
\item reveal.md, impress.js (for making presentations)
\end{enumerate} 

\section{Future Scope}                                                  
This software being a open source have allot of scope for future improvements
and additions as other individuals can also contibute in it and add additional functionality
like-:                                                                  
\begin{enumerate}                                                       
\item Convert parser code (presently it is in C++) to Flex and Bison language                                 
\item Making builing from Staad Pro file                     
\item Convert Staad Pro file to IFC (Industry Foundation Classes) and then rendering IFC with different opensource viewer on the browser.                              
\item BIM integration
\item Adding dimensions to the output drawing
\end{enumerate}  
